### 2023-12-03 main.tex
densities

{\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form. On the other hand, absorption probabilities are hard to to find since they fulfil multilinear algebraic equation with proper boundary conditions. The situation simplifies when the graph reduces to a chain with two reservoirs on the boundary sites. In this context, the integrable structure of the process can be combined with duality to compute non-equilibrium steady state. Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.}
{\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
% However,  for the case of integrable systems they can be computed exactly in closed-form.

@@

\noindent
\begin{remark}
\label{hole}
In the following we will often consider type $N$ as a distinguished type
(called `holes'), whose number at each site is fixed by the numbers of particles 
of the remaining $N-1$ types. 
% It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
% (those of types $\{1,\ldots,N-1\}$), we retrieve the 
% boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
In the case $N=2$, we retrieve the  boundary-driven version of the symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
% \todo{I would prefer to say this is for N=2}
The choice of type $N$ for the distinguished type is arbitrary and does not affect
the results. However, we shall see in Section~\ref{sectionDuality}, that
the dual process breaks the symmetry.
In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
\end{remark}
\todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}

@@

If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost: 
each reservoir at site $x$ {\color{red}wants to fix}\todo{?} its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with

@@

and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$.
Currents will arise when at least two reservoirs have different densities. 

@@

		One can check that the following condition on the reservoir parameters implies reversibility:

@@

		This is slightly more general than \eqref{reversibilityCondition}. In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites

@@

@@

>>>>

{\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form. On the other hand, absorption probabilities are hard to find since they fulfil multilinear algebraic equation with proper boundary conditions. The situation simplifies when the graph reduces to a chain with two reservoirs on the boundary sites. In this context, the integrable structure of the process can be combined with duality to compute non-equilibrium steady state. Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.}
{\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
% However,  for the case of integrable systems they can be computed exactly in closed-form.

@@

%\noindent
%\begin{remark}
%\label{hole}
In the following we will often consider type $N$ as a distinguished type
(called `holes'), whose number at each site is fixed by the numbers of particles 
of the remaining $N-1$ types. 
% It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
% (those of types $\{1,\ldots,N-1\}$), we retrieve the 
% boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
In the case $N=2$, we retrieve the  boundary-driven version of the symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
% \todo{I would prefer to say this is for N=2}
The choice of type $N$ for the distinguished type is arbitrary and does not affect
the results. However, we shall see in Section~\ref{sectionDuality}, that
the dual process breaks the symmetry.
In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
%\end{remark}
\todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}
{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
Second question: I think yes. The concept of boundary is general, not only for the chain}

@@

If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost: indeed, in this situation, each reservoir at site $x$ has  its own set of densities vector $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with components

@@

and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$. {\color{blue} As a consequence, particles are injected and removed in the graph with different rates. When, for any $a\in \{1,\ldots,N\}$ there are at least two reservoirs at sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility. Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}
\todo{?}
%Currents will arise when at least two reservoirs have different densities. 

@@

		{\color{blue}One can check that conditions \eqref{reversibilityCondition} are not the most general that implies reversibility. Indeed, by choosing the reservoir parameters as }

@@

		reversibility holds. 
		%This is slightly more general than \eqref{reversibilityCondition}.
		 In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites

@@

{\color{blue}where the expectation is take with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}

@@

\begin{equation}%\label{exactCorrelations}
